\subsection{Current Implementation}
\begin{itemize}[leftmargin=*]
    \item Instead of an appointment booking system, users will be shown basic business information, including:
    \begin{itemize}
        \item \textbf{Business Name:} Display the name of the business.
        \item \textbf{Contact Details:} Provide phone numbers or email addresses for direct communication.
        \item \textbf{Address:} Show the physical location of the business.
    \end{itemize}
    \item Customers can directly contact businesses to inquire about services or book appointments manually.
\end{itemize}

\subsection{Deferred Features}
\begin{itemize}[leftmargin=*]
    \item \textbf{Appointment Booking Flow:}
    \begin{itemize}
        \item \textbf{Date/Time Selection:}
        \begin{itemize}
            \item Implement a calendar interface for customers to select dates.
            \item Display available time slots based on staff availability and service duration.
            \item Allow customers to choose preferred staff members if desired.
        \end{itemize}
        
        \item \textbf{Service Selection:}
        \begin{itemize}
            \item Provide a list of available services with detailed descriptions and pricing.
            \item Enable filtering by service categories and subcategories.
            \item Allow customers to select multiple services in a single booking session.
        \end{itemize}
        
        \item \textbf{Basic Availability Checking:}
        \begin{itemize}
            \item Real-time availability checking to prevent double bookings.
            \item Consideration of staff working hours, breaks, and holidays.
            \item Automatic updates to availability upon booking confirmation.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Appointment Management:}
    \begin{itemize}
        \item \textbf{View, Modify, or Cancel Appointments:}
        \begin{itemize}
            \item Provide customers with a dashboard to view upcoming and past appointments.
            \item Allow modifications to appointment details, including rescheduling and service changes.
            \item Implement cancellation policies and fees, if applicable.
        \end{itemize}
        
        \item \textbf{Status Updates:}
        \begin{itemize}
            \item Appointment statuses include Pending, Confirmed, Completed, and Cancelled.
            \item Automatic status updates based on business rules (e.g., auto-confirmation after a set period).
            \item Notifications sent to customers and staff upon status changes.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Email Notifications:}
    \begin{itemize}
        \item \textbf{Booking Confirmation:}
        \begin{itemize}
            \item Send confirmation emails to customers upon successful booking.
            \item Include appointment details, such as date, time, services, and staff.
        \end{itemize}
        
        \item \textbf{Appointment Reminders:}
        \begin{itemize}
            \item Schedule reminder emails to be sent 24 hours and 1 hour before appointments.
            \item Allow customers to customize reminder settings.
        \end{itemize}
        
        \item \textbf{Status Changes:}
        \begin{itemize}
            \item Notify customers of any changes in appointment status (e.g., cancellations or rescheduling).
            \item Provide links for quick access to appointment management in the email.
        \end{itemize}
    \end{itemize}
\end{itemize}


