\subsection{User Authentication System}
\begin{itemize}[leftmargin=*]
    \item \textbf{Customer Authentication:}
    \begin{itemize}
        \item \textbf{JWT-based Authentication:} Implement JSON Web Tokens for secure session management, with refresh tokens for session renewal.
        \item \textbf{Email Verification:} Use SendGrid to send verification emails upon signup, ensuring valid email addresses.
        \item \textbf{Rate Limiting:} Add rate limiting on login attempts to prevent brute force attacks, allowing a maximum of 5 attempts per 15 minutes.
            \item \textbf{Push Notifications:} Integrate push notifications to alert users about account activity, such as login from a new device or password changes, enhancing security and engagement.

    \end{itemize}
    
  
    
    \item \textbf{Profile Management:}
    \begin{itemize}
        \item \textbf{Profile Picture Upload:} Integrate with AWS S3 for storing and retrieving user profile pictures.
        \item \textbf{Contact Information Management:} Allow users to update their contact details, including phone numbers and addresses.
        \item \textbf{Notification Preferences:} Enable users to set preferences for receiving notifications via email.
    \end{itemize}
    
    \item \textbf{Security Features:}
    \begin{itemize}
        \item \textbf{Password Strength Requirements:} Enforce strong passwords with a minimum of 8 characters, including special characters and numbers.
        \item \textbf{Password Hashing:} Use bcrypt for hashing passwords, ensuring secure storage.
        \item \textbf{Session Management:} Implement token expiration and renewal mechanisms for secure session handling.
    \end{itemize}
\end{itemize}

\subsection{Deferred for Future Implementation}

\begin{itemize}[leftmargin=*]
  \item \textbf{Business Authentication:}
    \begin{itemize}
        \item \textbf{Separate Authentication Flow:} Provide a simple, tailored authentication process for businesses.
        \item \textbf{Business Verification:} Implement a basic admin approval process for business accounts.
    \end{itemize}
    \item \textbf{OAuth Integration:} Integration with Google and Facebook for social login.
    \item \textbf{Multi-factor Authentication:} Provide additional security options for businesses.
    \item \textbf{Advanced Admin Panel:} Develop a comprehensive admin interface for managing business approvals and monitoring account status.

    \item \textbf{Notification Preferences via SMS:} Extend notification preferences to include SMS.
    \item \textbf{CSRF Protection:} Use anti-CSRF tokens for cross-site request forgery prevention.
    \item \textbf{Account Deletion:} Implement a fully compliant process for users to request account deletion in line with data protection regulations.
\end{itemize}
