\subsection{Service History}
\begin{itemize}[leftmargin=*]
    \item \textbf{View Past Services:}
    \begin{itemize}
        \item Provide customers with a history of all services availed.
        \item Include details such as service names, dates, staff members, and costs.
        \item Allow customers to reorder past services with a single click.
    \end{itemize}
    
    \item \textbf{Service Feedback:}
    \begin{itemize}
        \item Enable customers to provide feedback or ratings for past services.
        \item Display average ratings and reviews for each service.
        \item Allow customers to edit or delete their reviews within a set timeframe.
    \end{itemize}
\end{itemize}

\subsection{Consultation Form}
\begin{itemize}[leftmargin=*]
    \item \textbf{Basic Consultation Form:}
    \begin{itemize}
        \item Provide a form for customers to fill out prior to appointments.
        \item Include fields for personal preferences, allergies, and special requests.
        \item \textbf{Deferred:} Allow businesses to customize the form based on service type.
    \end{itemize}
    
    \item \textbf{Form Submission and Review:}
    \begin{itemize}
        \item Enable customers to submit the form online before appointments.
        \item Allow staff to review and update form details as needed.
        \item Store form submissions securely with customer profiles.
    \end{itemize}
\end{itemize}

\subsection{Rating/Review System}
\begin{itemize}[leftmargin=*]
    \item \textbf{Simple Rating System:}
    \begin{itemize}
        \item Allow customers to rate services and staff members on a 5-star scale.
        \item Display average ratings prominently on service and staff profiles.
        \item Enable businesses to respond to customer reviews.
    \end{itemize}
    
    \item \textbf{Review Moderation [Deferred]:}
    \begin{itemize}
        \item Implement moderation tools to filter inappropriate content.
        \item Allow flagged reviews to be reviewed by admin before publication.
        \item Notify customers when their review is published or flagged.
    \end{itemize}
\end{itemize}

\subsection{Upcoming Appointments}
\begin{itemize}[leftmargin=*]
    \item \textbf{Appointment Dashboard:}
    \begin{itemize}
        \item Provide a dashboard for customers to view upcoming appointments.
        \item Include options to modify, cancel, or reschedule appointments.
        \item Display appointment details such as date, time, services, and staff.
    \end{itemize}
    
    \item \textbf{Calendar Integration [Deferred]:}
    \begin{itemize}
        \item Allow customers to sync appointments with personal calendars (e.g., Google Calendar).
        \item Send calendar invites with appointment details and reminders.
        \item Provide options to update calendar entries upon appointment changes.
    \end{itemize}
\end{itemize}
