\begin{thebibliography}{99}

\bibitem{expo-docs}
Expo Documentation,  
\textit{Expo: The official documentation for building cross-platform apps with React Native.}  
Available at: \url{https://docs.expo.dev/}

\bibitem{expo-github}
Expo GitHub Repository,  
\textit{Source code and issues for the Expo platform.}  
Available at: \url{https://github.com/expo/expo}

\bibitem{react-native-docs}
React Native Documentation,  
\textit{Getting started with React Native for mobile development.}  
Available at: \url{https://reactnative.dev/docs/getting-started}

\bibitem{react-native-github}
React Native GitHub Repository,  
\textit{Official source code and examples for React Native.}  
Available at: \url{https://github.com/facebook/react-native}

\bibitem{styled-components}
Styled Components Documentation,  
\textit{Learn how to style your React components effectively.}  
Available at: \url{https://styled-components.com/docs}

\bibitem{nestjs-docs}
NestJS Documentation,  
\textit{Comprehensive guide for building scalable and maintainable server-side applications.}  
Available at: \url{https://docs.nestjs.com/}

\bibitem{graphql-docs}
GraphQL Documentation,  
\textit{Learn how to use GraphQL for efficient data querying.}  
Available at: \url{https://graphql.org/learn/}

\bibitem{aws-docs}
Amazon Web Services Documentation,  
\textit{Guides and resources for AWS services like ECS, S3, and CloudWatch.}  
Available at: \url{https://aws.amazon.com/documentation/}

\bibitem{typeorm-docs}
TypeORM Documentation,  
\textit{Guidance for managing relational databases with TypeORM.}  
Available at: \url{https://typeorm.io/}

\bibitem{wcagDocs}
World Wide Web Consortium (W3C). (2018). \textit{Web Content Accessibility Guidelines (WCAG) 2.1}. Retrieved from \url{https://www.w3.org/TR/WCAG21/}.

\bibitem{webAIMContrastChecker}
WebAIM. (2025). \textit{Color Contrast Checker}. Retrieved from \url{https://webaim.org/resources/contrastchecker/}.

\bibitem{ariaDocs}
World Wide Web Consortium (W3C). (2025). \textit{Accessible Rich Internet Applications (WAI-ARIA) 1.1}. Retrieved from \url{https://www.w3.org/TR/wai-aria/}.

\bibitem{responsiveDesignDocs}
Mozilla Developer Network. (2025). \textit{Responsive Design Basics}. Retrieved from \url{https://developer.mozilla.org/en-US/docs/Learn/CSS/CSS_layout/Responsive_Design}.

\bibitem{gdprDocs}
European Union. (2016). \textit{General Data Protection Regulation (GDPR)}. Retrieved from \url{https://eur-lex.europa.eu/eli/reg/2016/679/oj}.

\bibitem{ccpaDocs}
California Legislature. (2018). \textit{California Consumer Privacy Act (CCPA)}. Retrieved from \url{https://oag.ca.gov/privacy/ccpa}.

\bibitem{encryptionStandards}
National Institute of Standards and Technology (NIST). (2025). \textit{AES: Advanced Encryption Standard (FIPS PUB 197)}. Retrieved from \url{https://nvlpubs.nist.gov/nistpubs/FIPS/NIST.FIPS.197.pdf}.

\bibitem{vulnerabilityScanning}
OWASP Foundation. (2025). \textit{OWASP Top 10: Web Application Security Risks}. Retrieved from \url{https://owasp.org/www-project-top-ten/}.

\bibitem{penetrationTesting}
The Open Source Security Testing Methodology Manual (OSSTMM). (2025). \textit{A Guide to Penetration Testing}. Retrieved from \url{https://www.isecom.org/OSSTMM/}.

\bibitem{mfaImplementation}
Microsoft. (2025). \textit{Guide to Implementing Multi-Factor Authentication (MFA)}. Retrieved from \url{https://docs.microsoft.com/en-us/azure/active-directory/authentication/concept-mfa-howitworks}.

\bibitem{incidentResponse}
National Institute of Standards and Technology (NIST). (2021). \textit{Computer Security Incident Handling Guide (SP 800-61 Rev. 2)}. Retrieved from \url{https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-61r2.pdf}.

\bibitem{keyboardAccessibility}
Deque Systems. (2025). \textit{Keyboard Accessibility Guide}. Retrieved from \url{https://www.deque.com/keyboard-accessibility/}.

\bibitem{mobileAccessibility}
Google. (2025). \textit{Android Accessibility Developer Checklist}. Retrieved from \url{https://developer.android.com/guide/topics/ui/accessibility}.

\bibitem{screenReaderTesting}
Apple. (2025). \textit{VoiceOver User Guide for macOS}. Retrieved from \url{https://support.apple.com/guide/voiceover/welcome/mac}.

\bibitem{secureCoding}
OWASP Foundation. (2025). \textit{Secure Coding Practices}. Retrieved from \url{https://owasp.org/www-project-secure-coding-practices/}.


\end{thebibliography}