\subsection{Appointment Calendar View [Deferred]}
\begin{itemize}[leftmargin=*]
    \item \textbf{Interactive Calendar:}
    \begin{itemize}
        \item Provide an interactive calendar view for businesses to manage appointments.
        \item Display appointments in a daily, weekly, or monthly view.
        \item Allow color-coding of appointments based on status (e.g., confirmed, pending).
    \end{itemize}
    
    \item \textbf{Drag-and-Drop Rescheduling :}
    \begin{itemize}
        \item Enable drag-and-drop functionality for easy rescheduling of appointments.
        \item Automatically update appointment details and notify customers of changes.
        \item Implement conflict detection to prevent overlapping appointments.
    \end{itemize}
\end{itemize}

\subsection{Daily Schedule View [Deferred or Not Included]}
\begin{itemize}[leftmargin=*]
    \item \textbf{Staff Schedules:}
    \begin{itemize}
        \item Display individual staff schedules with assigned appointments and breaks.
        \item Allow staff to update their availability directly from the dashboard.
        \item Highlight any gaps or overbooked slots for quick adjustments.
    \end{itemize}
    
    \item \textbf{Service Overview:}
    \begin{itemize}
        \item Provide a summary of services scheduled for the day, including customer details.
        \item Allow businesses to print or export daily schedules for offline access.
        \item Include quick access links to customer profiles and service details.
    \end{itemize}
\end{itemize}

\subsection{Basic Customer List [Deferred]}
\begin{itemize}[leftmargin=*]
    \item \textbf{Customer Directory:}
    \begin{itemize}
        \item Maintain a directory of all customers with key information such as contact details and service history.
        \item Enable search and filter options for quick retrieval of customer data.
        \item Allow businesses to add notes or tags to customer profiles for personalized service.
    \end{itemize}
    
    \item \textbf{Customer Engagement:}
    \begin{itemize}
        \item Provide tools for sending personalized messages or promotions to customers.
        \item Track customer interactions and engagement metrics.
        \item Enable integration with CRM systems for advanced customer management.
    \end{itemize}
\end{itemize}

\subsection{Simple Service Management Interface [Deferred]}
\begin{itemize}[leftmargin=*]
    \item \textbf{Service Catalog Management:}
    \begin{itemize}
        \item Allow businesses to add, edit, or remove services from their catalog.
        \item Provide tools for updating service descriptions, pricing, and availability.
        \item Implement bulk editing features for managing multiple services at once.
    \end{itemize}
    
    \item \textbf{Performance Analytics:}
    \begin{itemize}
        \item Display analytics on service performance, including booking trends and revenue.
        \item Highlight top-performing services and identify areas for improvement.
        \item Allow businesses to export analytics reports for further analysis.
    \end{itemize}
\end{itemize}