\subsection{Business Profile System}
\begin{itemize}[leftmargin=*]
    \item \textbf{Manually Stored Information:}
    \begin{itemize}
        \item \textbf{Business Name:} Store the business name in the database for reference.
        \item \textbf{Business Address:} Maintain a record of the physical address of businesses.
        \item \textbf{Contact Details:} Store contact numbers manually in the database.
    \end{itemize}
\end{itemize}

\subsection{Deferred for Future Implementation}
\begin{itemize}[leftmargin=*]
    \item \textbf{Profile Information:}
    \begin{itemize}
        \item \textbf{Business Name and Description:} Allow businesses to enter a name and a brief description that highlights their services and specialties.
        \item \textbf{Multiple Contact Numbers:} Enable businesses to provide multiple contact numbers for different departments or purposes.
        \item \textbf{Business Category Selection:} Provide a list of predefined categories (e.g., Hair, Makeup, Spa) for businesses to classify their services.
        \item \textbf{Business Hours with Timezone Support:} Enable businesses to set their operating hours, including support for different time zones.
        \item \textbf{Physical Address with Geocoding:} Integrate with a geocoding API to convert physical addresses into geographical coordinates for map-based features.
        \item \textbf{Social Media Links:} Allow businesses to add links to their social media profiles to increase customer engagement.
        \item \textbf{Holiday Schedule Management:} Allow businesses to specify holidays or special closing days to manage customer expectations.
    \end{itemize}

    \item \textbf{Team Management:}
    \begin{itemize}
        \item \textbf{Staff Profiles with Roles:} Create profiles for each staff member, assigning roles such as admin, stylist, or receptionist.
        \item \textbf{Service Assignment to Staff Members:} Allow businesses to assign specific services to staff members based on their expertise.
        \item \textbf{Individual Staff Calendars:} Provide each staff member with a personal calendar to manage their appointments and availability.
        \item \textbf{Staff Availability Management:} Enable businesses to manage staff availability, including setting working hours and break times.
    \end{itemize}

    \item \textbf{Service Management:}
    \begin{itemize}
        \item \textbf{Service Categories and Subcategories:} Organize services into categories and subcategories for easier navigation and selection by customers.
        \item \textbf{Duration Settings with Buffer Time:} Enable businesses to specify the duration of services, including buffer time for preparation or cleanup.
        \item \textbf{Service Description and Requirements:} Provide fields for detailed service descriptions and any prerequisites or requirements for customers.
        \item \textbf{Pricing Tiers:} Allow businesses to set different pricing tiers (e.g., basic, premium) for their services.
        \item \textbf{Before/After Photos for Services:} Allow businesses to upload before and after photos to showcase the effectiveness of their services.
        \item \textbf{Bulk Service Import/Export:} Facilitate the import and export of service lists for businesses with extensive catalogs.
    \end{itemize}
\end{itemize}
