The Community Page within the BEAUT AI app serves as a dedicated social platform for users to engage with medical aesthetic treatments, businesses offering these services, and other members. Users can share personal experiences, posts, and photos about medical aesthetic treatments, interact with businesses, and explore beauty-related content. This section will include features for discussions, sharing content, user engagement, and business visibility.

\subsection{User Profiles}
\begin{itemize}
    \item \textbf{Customizable User Profiles:}
    \begin{itemize}
        \item Each user can create and maintain a personalized profile showcasing their treatment preferences, past medical aesthetic treatments, and favorite businesses.
        \item Profiles can include a photo, short bio, and a gallery of shared medical aesthetic treatment experiences (images, videos, reviews).
        \item Users can set privacy settings for each profile section (e.g., whether their shared content is public or restricted to certain users).
    \end{itemize}
    
    \item \textbf{Past Treatments and Businesses:}
    \begin{itemize}
        \item Display a history of medical aesthetic treatments that users have received, including ratings and reviews.
        \item Business names and profiles providing treatments will be linked to posts or reviews made by users.
        \item Allow users to tag businesses in their posts to improve visibility and business engagement.
    \end{itemize}
\end{itemize}

\subsection{Sharing Content and Interaction}
\begin{itemize}
    \item \textbf{Treatment Posts:}
    \begin{itemize}
        \item Users can share posts that include images, videos, and descriptions of the medical aesthetic treatments they have received or are recommending.
        \item Posts will allow users to mention specific medical aesthetic treatments (e.g., facials, skin rejuvenation, body contouring), and link them to businesses offering these services.
        \item Each post can include user-generated content like "Before \& After" images to show the effectiveness of treatments.
    \end{itemize}
    
    \item \textbf{Business Visibility:}
    \begin{itemize}
        \item When a user posts about a treatment, the business that provided the treatment is automatically tagged and visible in the post.
        \item Businesses can claim their profiles to showcase their services, pricing, location, and customer reviews directly on the posts.
        \item Users can follow businesses to receive updates on promotions, new treatments, or special offers shared by the business on the community page.
    \end{itemize}
    
    \item \textbf{Likes, Comments, and Shares:}
    \begin{itemize}
        \item Users can like, comment, and share other users' posts.
        \item Each post will have an option to add comments, allowing users to interact and discuss treatments, businesses, or medical aesthetic topics.
        \item Shared posts allow users to spread content to their followers or in relevant community groups (e.g., treatment seekers, beauty enthusiasts).
    \end{itemize}
    
    \item \textbf{Hashtags and Categories:}
    \begin{itemize}
        \item Users can add hashtags to their posts to categorize treatments or trends (e.g., \#SkinRejuvenation, \#BodyContouring).
        \item Posts with common hashtags will appear in trending sections, making it easier for users to discover popular treatments or trending topics.
    \end{itemize}
\end{itemize}

\subsection{Interaction with Businesses}
\begin{itemize}
    \item \textbf{Business Profiles:}
    \begin{itemize}
        \item Businesses offering medical aesthetic treatments can create detailed profiles showcasing their services, images, reviews, pricing, and available slots.
        \item Businesses can interact with customers by responding to comments, reviews, and questions posted by users.
        \item Provide businesses with the ability to post updates, promotions, or special offers that will be visible to users.
    \end{itemize}
    
    \item \textbf{Appointment Booking Integration:}
    \begin{itemize}
        \item Directly link from business posts or profiles to booking pages where users can schedule appointments for medical aesthetic treatments.
        \item Businesses can display availability and offer discounts or promotions through the community platform.
    \end{itemize}
    
    \item \textbf{User Reviews and Ratings:}
    \begin{itemize}
        \item Users can rate and leave feedback on businesses and treatments they’ve experienced.
        \item Review sections will include star ratings, textual feedback, and the ability to upload pictures of treatments.
        \item Businesses can reply to reviews, addressing customer feedback or thanking users for their comments.
    \end{itemize}
\end{itemize}

\subsection{Content Discovery and Trending Topics}
\begin{itemize}
    \item \textbf{Explore Section:}
    \begin{itemize}
        \item A curated “Explore” section allows users to discover the latest medical aesthetic trends, new treatments, and top businesses based on their interests.
        \item Use personalized recommendations to highlight posts and businesses based on a user's activity, preferences, and engagement history.
    \end{itemize}
    
    \item \textbf{Trending Posts and Hashtags:}
    \begin{itemize}
        \item Trending posts will appear on the main feed, showcasing the most popular or highly engaged content, based on likes, shares, and comments.
        \item Trending hashtags will allow users to follow specific medical aesthetic trends, services, or treatment types (e.g., \#AntiAging, \#FacialRejuvenation).
    \end{itemize}
    
    \item \textbf{Follow Users and Businesses:}
    \begin{itemize}
        \item Users can follow other community members who share interesting content or have valuable insights.
        \item Businesses can be followed for updates about new services, promotions, or events.
    \end{itemize}
\end{itemize}

\subsection{Event and Webinar Integration}
\begin{itemize}
    \item \textbf{Medical Aesthetic Events:}
    \begin{itemize}
        \item Users can participate in community-hosted medical aesthetic events, webinars, or live Q\&A sessions with beauty experts and professionals.
        \item Events can be promoted via posts and business profiles, with details on how to register, topics covered, and speakers.
    \end{itemize}
    
    \item \textbf{Live Streaming:}
    \begin{itemize}
        \item Businesses can stream live medical aesthetic tutorials, product demonstrations, or customer reviews directly on the community page.
        \item Users can interact with live sessions by commenting, asking questions, and engaging in real-time.
    \end{itemize}
\end{itemize}

\subsection{Privacy and Moderation}
\begin{itemize}
    \item \textbf{Content Moderation:}
    \begin{itemize}
        \item All posts and comments are subject to moderation to ensure the content is appropriate and follows community guidelines.
        \item Users can report inappropriate or harmful content that will be reviewed by administrators.
    \end{itemize}
    
    \item \textbf{Privacy Controls:}
    \begin{itemize}
        \item Users can manage the visibility of their content and choose to share posts only with selected followers, specific groups, or keep them private.
        \item Profile privacy settings will allow users to control who can view their shared content, send messages, or comment on their posts.
    \end{itemize}
    
    \item \textbf{User Blocking and Reporting:}
    \begin{itemize}
        \item Users can block other members or report content that violates community rules, including spam, offensive language, or misleading information.
    \end{itemize}
\end{itemize}

\subsection{User Engagement and Rewards}
\begin{itemize}
    \item \textbf{Badges and Recognition:}
    \begin{itemize}
        \item Users can earn badges and rewards for participating actively in the community (e.g., "Top Reviewer," "Aesthetic Guru").
        \item Badges can be displayed on user profiles to highlight their contributions to the community.
    \end{itemize}
    
    \item \textbf{Incentives for Content Creators:}
    \begin{itemize}
        \item Reward users who consistently post high-quality content with exclusive benefits, such as discounts on treatments or access to VIP events.
        \item Offer incentives like referral bonuses or points for sharing content that leads to bookings or customer referrals.
    \end{itemize}
    
\end{itemize}

\subsection{Prerequisite Functionalities for Community Page Development}
\begin{itemize}
    \item \textbf{User Authentication and Profile Management:}
    \begin{itemize}
        \item Implement secure user authentication using \texttt{OAuth 2.0}, \texttt{JWT (JSON Web Tokens)}, or \texttt{Session-based Authentication}.
        \item Use frameworks like \texttt{Firebase Authentication}, \texttt{Passport.js} (for Node.js), or \texttt{Django Allauth} (for Python).
        \item Develop customizable user profiles stored in a database like \texttt{MongoDB}, \texttt{PostgreSQL}, or \texttt{MySQL}.
        \item Use libraries like \texttt{Cloudinary} or \texttt{Amazon S3} for secure media storage (e.g., profile photos).
        \item Integrate role-based access controls (\texttt{RBAC}) for privacy level management.
    \end{itemize}
    
    \item \textbf{Content Posting and Sharing System:}
    \begin{itemize}
        \item Use a rich text editor such as \texttt{Quill.js} or \texttt{TinyMCE} for creating posts.
        \item Store multimedia content securely using \texttt{AWS S3}, \texttt{Google Cloud Storage}, or \texttt{Cloudinary}.
        \item Implement tagging with a database schema that supports many-to-many relationships (e.g., in \texttt{PostgreSQL} or \texttt{MongoDB}).
        \item Use \texttt{GraphQL} or \texttt{RESTful APIs} to handle media uploads and linking posts to businesses.
    \end{itemize}
    
    \item \textbf{Interaction Features:}
    \begin{itemize}
        \item Enable liking and commenting using real-time databases like \texttt{Firebase Firestore} or \texttt{Redis}.
        \item Implement discussion threads with hierarchical data models in \texttt{NoSQL} or tree structures in \texttt{SQL}.
        \item Develop notification systems using \texttt{WebSockets} (e.g., \texttt{Socket.IO}) or third-party services like \texttt{OneSignal}.
    \end{itemize}
    
    \item \textbf{Business Integration and Profiles:}
    \begin{itemize}
        \item Use \texttt{Google Maps API} or \texttt{Mapbox} for business location integration.
        \item Store business information and reviews in a relational database such as \texttt{PostgreSQL} or \texttt{MySQL}.
        \item Implement authentication and verification for businesses using \texttt{SendGrid} or \texttt{Twilio}.
        \item Enable interactions with user posts and reviews using APIs with \texttt{GraphQL} or \texttt{REST}.
    \end{itemize}
    
    \item \textbf{Content Discovery and Categorization:}
    \begin{itemize}
        \item Build an explore section powered by recommendation algorithms using \texttt{Python} libraries like \texttt{scikit-learn} or \texttt{TensorFlow}.
        \item Store hashtags and trending data in a NoSQL database like \texttt{MongoDB} or \texttt{Elasticsearch}.
        \item Implement personalized feeds using \texttt{Collaborative Filtering} or \texttt{Content-based Filtering}.
    \end{itemize}
    
    \item \textbf{Event and Webinar Support:}
    \begin{itemize}
        \item Use \texttt{WebRTC} for live streaming capabilities or integrate platforms like \texttt{Zoom API}.
        \item Enable event scheduling and tracking using \texttt{Google Calendar API} or \texttt{Microsoft Graph API}.
        \item Store event details and user participation data in a relational database such as \texttt{PostgreSQL}.
    \end{itemize}
    
    \item \textbf{Privacy and Moderation Tools:}
    \begin{itemize}
        \item Implement content moderation using \texttt{AI-based tools} like \texttt{AWS Rekognition} or \texttt{Google Vision API} for detecting inappropriate images.
        \item Add user reporting and blocking functionalities with flagging systems managed in \texttt{Redis} or \texttt{MongoDB}.
        \item Enable privacy settings using a rules engine with \texttt{Spring Security} (Java) or \texttt{Express Middleware} (JavaScript).
    \end{itemize}

    \item \textbf{User Engagement and Rewards System:}
    \begin{itemize}
        \item Develop a badge system using \texttt{DynamoDB} for quick reads and writes or \texttt{Firestore} for scalable storage.
        \item Create incentive programs integrated with payment gateways like \texttt{Stripe API} or \texttt{PayPal SDK}.
    \end{itemize}
\end{itemize}

