\subsection{Accessibility Standards}
\begin{itemize}[leftmargin=*]
    \item \textbf{WCAG Compliance:}
    \begin{itemize}
        \item Adhere to WCAG 2.1 Level A and AA standards to ensure accessibility for users with disabilities.
        \item Implement keyboard navigation and screen reader compatibility across the application.
        \item Use semantic HTML and ARIA roles to enhance accessibility features.
    \end{itemize}
    
    \item \textbf{Mobile Accessibility:}
    \begin{itemize}
        \item Ensure touch targets are appropriately sized and spaced for mobile users.
        \item Support voiceover and screen reader functionalities on both iOS and Android.
        \item Implement gesture-based navigation and interactions where applicable.
    \end{itemize}
    
    \item \textbf{Color Contrast:}
    \begin{itemize}
        \item Ensure sufficient color contrast between text and background elements.
        \item Use tools like the WebAIM Color Contrast Checker to validate compliance.
        \item Provide alternative text for images and non-text content.
    \end{itemize}
    
    \item \textbf{Responsive Design:}
    \begin{itemize}
        \item Design the application to be fully responsive across devices and screen sizes.
        \item Use flexible grid layouts and media queries to adapt to different viewports.
        \item Test responsiveness on a range of devices, including mobile, tablet, and desktop.
    \end{itemize}
\end{itemize}

\subsection{Data Protection and Privacy Compliance}
\begin{itemize}[leftmargin=*]
    \item \textbf{GDPR Compliance:}
    \begin{itemize}
        \item Implement mechanisms for obtaining user consent for data collection and processing.
        \item Provide users with the ability to access, rectify, and delete their personal data.
        \item Maintain records of processing activities and data protection impact assessments.
    \end{itemize}
    
    \item \textbf{CCPA Compliance:}
    \begin{itemize}
        \item Allow California residents to opt-out of the sale of their personal information.
        \item Provide clear and transparent privacy notices detailing data collection practices.
        \item Implement processes for responding to consumer rights requests within mandated timeframes.
    \end{itemize}
    
    \item \textbf{Data Encryption:}
    \begin{itemize}
        \item Encrypt sensitive data both at rest and in transit using industry-standard protocols.
        \item Use secure key management practices to protect encryption keys.
        \item Regularly audit encryption implementations to ensure compliance with best practices.
    \end{itemize}
\end{itemize}

\subsection{Security Measures}
\begin{itemize}[leftmargin=*]
    \item \textbf{Vulnerability Management:}
    \begin{itemize}
        \item Conduct regular vulnerability assessments and penetration testing.
        \item Use automated tools to scan for common security vulnerabilities.
        \item Implement a patch management process to address identified vulnerabilities promptly.
    \end{itemize}
    
    \item \textbf{Access Controls:}
    \begin{itemize}
        \item Implement role-based access control (RBAC) to restrict access to sensitive data and functions.
        \item Use multi-factor authentication (MFA) for administrative access.
        \item Regularly review and update access permissions based on user roles and responsibilities.
    \end{itemize}
    
    \item \textbf{Incident Response:}
    \begin{itemize}
        \item Develop an incident response plan to address security breaches and data incidents.
        \item Conduct regular incident response drills to ensure preparedness.
        \item Maintain a communication plan for notifying affected parties and regulatory bodies in case of a breach.
    \end{itemize}
\end{itemize}
