These features are not essential for the initial launch and can be deferred for future phases. Below is a list with reasons for deferring each feature:  
\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item \textbf{Language Toggle}: While multilingual support can broaden the user base, it requires significant translation efforts and additional testing to ensure proper functionality across all supported languages. It can be introduced once the primary features are stable and localized demand is established.  
    % \item \textbf{Push Notifications}: Push notifications are valuable for engagement but require additional backend setup and integration with mobile platforms. For the MVP, email notifications will suffice for user communication.  
    % \item \textbf{Community Features}: Community elements like forums or user groups can be impactful but are not critical to core business operations or booking functionality. These can be added in later phases as the user base grows.  
    \item \textbf{Advanced Animations}: While advanced animations enhance user experience, they can increase development time and are not vital to delivering core functionality. Basic, responsive design will ensure usability for MVP.  
    \item \textbf{Full HIPAA Compliance}: Achieving full compliance involves rigorous testing, auditing, and infrastructure adjustments, which can be resource-intensive. Basic data protection and secure handling practices will suffice for the MVP to ensure a quick go-to-market strategy.  
    \item \textbf{ML/Computer Vision Features}: Implementing advanced features like machine learning or computer vision requires a significant amount of data and development resources. These can be explored in the future when the platform has a robust dataset and user adoption.  
    \item \textbf{Advanced Map Integration}: While features like dynamic routing or geolocation can improve user experience, they require third-party integrations and additional testing. Basic location-based search is sufficient for the MVP.  
    \item \textbf{Social Features}: Social elements like sharing services or connecting with other users add complexity without directly impacting the core functionality. These can be introduced as value-added features in subsequent updates.  
    \item \textbf{Advanced Analytics}: Advanced analytics for user behavior and trends require significant backend support and data infrastructure. For the MVP, basic analytics will provide sufficient insights into user engagement and system performance.  
\end{itemize}
By focusing on core functionality for the MVP, we can ensure timely delivery while keeping the product scalable for future enhancements.


% \section{Timeline Estimates (4 Experienced Developers)}
% \subsection{Week 1: Infrastructure \& Setup}
% \begin{itemize}[leftmargin=*]
%     \item \textbf{Team 1 (DevOps):}
%     \begin{itemize}
%         \item AWS infrastructure setup using Terraform
%         \item CI/CD pipeline configuration
%         \item Docker containerization
%         \item Monitoring setup (CloudWatch, Grafana)
%     \end{itemize}
    
%     \item \textbf{Team 2 (Backend):}
%     \begin{itemize}
%         \item NestJS project structure
%         \item Database schema design
%         \item Basic API setup with GraphQL
%         \item Authentication middleware
%     \end{itemize}
    
%     \item \textbf{Team 3 (Frontend):}
%     \begin{itemize}
%         \item React project setup with TypeScript
%         \item Component library selection
%         \item Routing setup
%         \item Basic layout implementation
%     \end{itemize}
    
%     \item \textbf{Team 4 (Full-stack):}
%     \begin{itemize}
%         \item Email service integration
%         \item Storage service setup
%         \item Logging system implementation
%         \item Error handling framework
%     \end{itemize}
% \end{itemize}
% % \subsection{Week 2: Core Features Development}
% \begin{itemize}
% \setlength{\itemsep}{0.1em}
%     \item Setup \& Infrastructure: 1 week
%     \item Auth \& User Management: 1 week
%     \item Business Management: 1 week
%     \item Appointment System: 1 week
%     \item Search \& Discovery: 1 week
%     \item Customer Features: 1 week
%     \item Business Dashboard: 1 week
%     \item Testing \& QA: 1 week
%     \item Deployment \& Launch Prep: 1 week
% \end{itemize}

% \textbf{Total estimated timeline: 6-8 weeks}

% Note: These timelines assume four full-time developers with at least 5 years of experience working together, and include buffer for testing and iterations.

