\subsection{AWS Services}
\begin{itemize}[leftmargin=*]
    \item \textbf{Compute Services:}
    \begin{itemize}
        \item Use Amazon EC2 for scalable virtual server instances.
        \item Deploy containerized applications using Amazon ECS or EKS.
        \item Implement auto-scaling groups to adjust resources based on demand.
    \end{itemize}
    
    \item \textbf{Storage Services:}
    \begin{itemize}
        \item Use Amazon S3 for storing static assets and user-uploaded files.
        \item Implement lifecycle policies for efficient storage management.
        \item Enable versioning and cross-region replication for data redundancy.
    \end{itemize}
    
    \item \textbf{Database Services:}
    \begin{itemize}
        \item Use Amazon RDS for MySQL as the primary relational database.
        \item Configure automated backups and multi-AZ deployments for high availability.
        \item Utilize Amazon DynamoDB for NoSQL storage needs, if applicable.
    \end{itemize}
    
    \item \textbf{Networking Services:}
    \begin{itemize}
        \item Use Amazon VPC to create a secure network environment.
        \item Implement Elastic Load Balancing (ELB) for distributing traffic.
        \item Configure AWS CloudFront as a content delivery network (CDN) for faster content delivery.
    \end{itemize}
\end{itemize}

\subsection{External Services}
\begin{itemize}[leftmargin=*]
    \item \textbf{Email Notifications:}
    \begin{itemize}
        \item Use SendGrid or AWS SES for sending transactional emails.
        \item Implement email templates for notifications, confirmations, and alerts.
        \item Monitor email delivery rates and handle bounces and complaints.
    \end{itemize}
    
    \item \textbf{Push Notifications:}
    \begin{itemize}
        \item Use Expo's push notification service for sending notifications to mobile devices.
        \item Implement user preferences for managing notification settings.
        \item Track notification delivery and engagement metrics.
    \end{itemize}
    
    \item \textbf{Monitoring and Logging:}
    \begin{itemize}
        \item Use AWS CloudWatch for real-time monitoring of application performance.
        \item Integrate with third-party tools like Datadog for enhanced monitoring capabilities.
        \item Implement centralized logging with AWS CloudWatch Logs or ELK Stack.
    \end{itemize}
\end{itemize}

\subsection{Security and Compliance}
\begin{itemize}[leftmargin=*]
    \item \textbf{Access Management:}
    \begin{itemize}
        \item Use AWS IAM for managing user access and permissions.
        \item Implement role-based access control (RBAC) for fine-grained permissions.
        \item Enable multi-factor authentication (MFA) for all administrative access.
    \end{itemize}
    
    \item \textbf{Data Protection:}
    \begin{itemize}
        \item Encrypt data at rest using AWS KMS or similar encryption services.
        \item Use SSL/TLS for encrypting data in transit.
        \item Regularly audit and review security policies and configurations.
    \end{itemize}
    
    \item \textbf{Compliance:}
    \begin{itemize}
        \item Ensure compliance with industry standards such as GDPR and CCPA.
        \item Conduct regular security assessments and vulnerability scans.
        \item Maintain documentation and records for compliance audits.
    \end{itemize}
\end{itemize}