\subsection{Basic Business Search}
\begin{itemize}[leftmargin=*]
    \item \textbf{List View of Businesses:}
    \begin{itemize}
        \item Display businesses in a list format with key information such as name, category, and rating.
        \item Include business logos or images for visual appeal.
        \item Implement pagination or infinite scroll for large result sets.
    \end{itemize}
    
    \item \textbf{Simple Filters:}
    \begin{itemize}
        \item Filter businesses by service type, location, and category.
        \item Provide options for filtering by business hours and availability.
        \item \textbf{Deferred:} Allow users to save filter preferences for future searches.
    \end{itemize}
    
    \item \textbf{Basic Sorting:}
    \begin{itemize}
        \item Sort businesses by distance from user's location, ratings, and popularity.
        \item \textbf{Deferred:} Implement sorting by price range and service availability.
        \item \textbf{Deferred:} Allow users to toggle between ascending and descending order.
    \end{itemize}
\end{itemize}

\subsection{Deferred Features}
\begin{itemize}[leftmargin=*]
    \item \textbf{Service Browsing:}
    \begin{itemize}
        \item \textbf{Filter by Category:}
        \begin{itemize}
            \item Display service categories prominently for easy navigation.
            \item Allow users to explore services within selected categories.
            \item Provide subcategory filters for more granular browsing.
        \end{itemize}
        
        \item \textbf{Price Range Filtering:}
        \begin{itemize}
            \item Enable users to set minimum and maximum price ranges for services.
            \item Display average pricing for selected services.
            \item Highlight promotions or discounts within the price range.
        \end{itemize}
        
        \item \textbf{Simple List View:}
        \begin{itemize}
            \item Present services in a clean, organized list with essential details.
            \item Include service descriptions, durations, and pricing.
            \item Allow users to add services to their favorites for quick access.
        \end{itemize}
    \end{itemize}
\end{itemize}

