\subsection{Service Type}  
\begin{itemize}  
    \item Each service is associated with a static business profile and includes key details such as:  
        \begin{itemize}  
            \item \textbf{Name}: The name of the service (e.g., Massage, Consultation).  
            \item \textbf{Description}: A detailed description of what the service offers.  
            \item \textbf{Duration}: The time required to complete the service (in minutes).  
            \item \textbf{Price}: The cost of the service.  
            \item \textbf{Category}: The category the service falls under (e.g., Health, Beauty, Fitness).  
            \item \textbf{Availability}: A list of available times for the service, linked to business availability.
        \end{itemize}
    \item Services are linked to static business profiles, allowing customers to browse available services per business.  
    \item Services are categorized to make browsing easier for users, enabling filtering and sorting by service type, category, or business.  
\end{itemize}

\subsection{Service Profile Linked to Business}  
\begin{itemize}  
    \item Each service is linked to a static business profile which includes:  
        \begin{itemize}  
            \item \textbf{Business Name}: The business offering the service.  
            \item \textbf{Business Location}: Physical address or online availability.  
            \item \textbf{Business Rating}: Customer reviews and ratings for the business.  
            \item \textbf{Service Hours}: Availability of services based on the business hours.
        \end{itemize}
    \item Services are dynamically displayed within business profiles to provide clear navigation for customers.  
    \item Businesses may offer different services within the same category, with each service being fully customizable.
\end{itemize}  

