\subsection{Performance Metrics}
\begin{itemize}[leftmargin=*]
    \item \textbf{App Load Time:}
    \begin{itemize}
        \item Target an average app load time of less than 3 seconds on mobile devices.
        \item Optimize asset delivery using Expo's asset management and caching strategies.
        \item Use performance profiling tools to identify and address bottlenecks.
    \end{itemize}
    
    \item \textbf{API Response Time:}
    \begin{itemize}
        \item Ensure API response times are consistently under 500 milliseconds.
        \item Implement query optimization and efficient data retrieval techniques.
        \item Use monitoring tools to track response times and identify slow endpoints.
    \end{itemize}
    
    \item \textbf{Uptime:}
    \begin{itemize}
        \item Achieve a service uptime of 99.9\% or higher.
        \item Use AWS CloudWatch and third-party services for uptime monitoring and alerts.
        \item Implement redundancy and failover strategies to minimize downtime.
    \end{itemize}
\end{itemize}

\subsection{Business Metrics}
\begin{itemize}[leftmargin=*]
    \item \textbf{User Acquisition:}
    \begin{itemize}
        \item Target 100 business signups and 1,000 customer signups in the first month.
        \item Track acquisition channels and conversion rates using analytics tools.
        \item Implement referral programs and promotions to boost signups.
    \end{itemize}
    
    \item \textbf{Booking Completion Rate:}
    \begin{itemize}
        \item Aim for an 80\% booking completion rate.
        \item Analyze drop-off points in the booking process and optimize user experience.
        \item Use A/B testing to test and refine booking flow enhancements.
    \end{itemize}
    
    \item \textbf{Customer Retention:}
    \begin{itemize}
        \item Monitor retention rates and identify factors influencing customer loyalty.
        \item Implement loyalty programs and personalized offers to increase retention.
        \item Use customer feedback to continuously improve service offerings.
    \end{itemize}
\end{itemize}

\subsection{User Engagement Metrics}
\begin{itemize}[leftmargin=*]
    \item \textbf{Active Users:}
    \begin{itemize}
        \item Track daily, weekly, and monthly active users.
        \item Analyze user engagement patterns and identify key usage trends.
        \item Use engagement metrics to inform feature development and prioritization.
    \end{itemize}
    
    \item \textbf{Session Duration:}
    \begin{itemize}
        \item Monitor average session duration to gauge user engagement.
        \item Identify content or features that drive longer sessions.
        \item Optimize user interface and content to encourage longer interactions.
    \end{itemize}
    
    \item \textbf{Feature Usage:}
    \begin{itemize}
        \item Track usage of key features such as booking, reviews, and messaging.
        \item Identify underutilized features and explore reasons for low engagement.
        \item Use feature usage data to prioritize updates and enhancements.
    \end{itemize}
    
    \item \textbf{App Downloads:}
    \begin{itemize}
        \item Monitor app download numbers from the Apple App Store and Google Play Store.
        \item Analyze download trends and the impact of marketing campaigns.
        \item Use download data to assess market reach and penetration.
    \end{itemize}
\end{itemize}