\subsection{Frontend}
\begin{itemize}[leftmargin=*]
    \item \textbf{Expo:}
    \begin{itemize}
        \item Use Expo for building cross-platform mobile applications with React Native.
        \item Leverage Expo's managed workflow for easy setup and development.
        \item Utilize Expo's libraries and APIs for accessing native device features.
    \end{itemize}
    
    \item \textbf{React Native:}
    \begin{itemize}
        \item Implement a component-based architecture for reusable UI components.
        \item Use React Hooks for managing state and side effects in functional components.
        \item Ensure responsive design and adaptation to various screen sizes and orientations.
    \end{itemize}
    
    \item \textbf{Styling:}
    \begin{itemize}
        \item Use Styled Components or React Native's StyleSheet for styling components.
        \item Implement a consistent design system with reusable styles and themes.
        \item Ensure accessibility and usability across different devices and platforms.
    \end{itemize}
    
    \item \textbf{State Management:}
    \begin{itemize}
        \item Use Redux or Context API for managing global state in the application.
        \item Implement middleware like Redux Thunk for handling asynchronous actions.
        \item Optimize state updates to improve performance and reduce re-renders.
    \end{itemize}
\end{itemize}

\subsection{Backend}
\begin{itemize}[leftmargin=*]
    \item \textbf{NestJS:}
    \begin{itemize}
        \item Use NestJS for building scalable and maintainable server-side applications.
        \item Implement a modular architecture with controllers, services, and modules.
        \item Use decorators and dependency injection for clean and organized code.
    \end{itemize}
    
    \item \textbf{GraphQL:}
    \begin{itemize}
        \item Use GraphQL for flexible and efficient data querying.
        \item Implement a schema-first approach with TypeScript for type safety.
        \item Use Apollo Server for GraphQL API implementation and integration.
    \end{itemize}
    
    \item \textbf{Authentication:}
    \begin{itemize}
        \item Implement JWT-based authentication for secure session management.
        \item Use Passport.js for integrating various authentication strategies.
        \item Ensure secure handling of authentication tokens and user credentials.
    \end{itemize}
\end{itemize}

\subsection{Database}
\begin{itemize}[leftmargin=*]
    \item \textbf{MySQL:}
    \begin{itemize}
        \item Use MySQL as the primary relational database for structured data storage.
        \item Implement normalization and indexing for optimized query performance.
        \item Use ORM tools like TypeORM for database interaction and migration management.
    \end{itemize}
    
    \item \textbf{Data Backup and Recovery:}
    \begin{itemize}
        \item Set up automated backups and snapshots for data protection.
        \item Implement disaster recovery strategies to ensure data availability.
        \item Regularly test backup and recovery processes to ensure reliability.
    \end{itemize}
\end{itemize}

\subsection{Cloud}
\begin{itemize}[leftmargin=*]
    \item \textbf{AWS:}
    \begin{itemize}
        \item Use AWS for scalable cloud infrastructure and services.
        \item Deploy applications using AWS ECS or EKS for container orchestration.
        \item Use AWS S3 for storing static assets and user-uploaded files.
    \end{itemize}
    
    \item \textbf{DevOps:}
    \begin{itemize}
        \item Implement CI/CD pipelines using AWS CodePipeline or Jenkins.
        \item Use Infrastructure as Code (IaC) tools like Terraform for resource provisioning.
        \item Monitor application performance and resource utilization with AWS CloudWatch.
    \end{itemize}
\end{itemize}

