\subsection{Mobile-Responsive Web Application}  
\begin{itemize}  
    \item Optimized for various screen sizes (desktop, tablet, and mobile).  
    \item Cross-browser compatibility (Chrome, Safari, Firefox, Edge).  
    \item Performance-focused design with a load time under 3 seconds.  
\end{itemize}  

\subsection{Expo Mobile App Requirements}  
\begin{itemize}  
    \item Platform Support:  
        \begin{itemize}  
            \item iOS (support for iOS 12 and above).  
            \item Android (support for Android 8.0 and above).  
        \end{itemize}  
    \item Responsiveness:  
        \begin{itemize}  
            \item Seamless layout scaling for various screen sizes and resolutions.  
            \item Device orientation support (portrait and landscape).  
        \end{itemize}  
    \item API Integration:  
        \begin{itemize}  
            \item Secure integration with backend services via GraphQL.  
            \item Real-time updates for appointment status and notifications.  
        \end{itemize}  
    \item Notifications:  
        \begin{itemize}  
            \item Push notifications using Expo’s notification service.  
            \item Configurable reminders for appointments and key updates.  
            \item Push notification settings for users to manage their preferences.  
        \end{itemize}  
    \item Offline Functionality:  
        \begin{itemize}  
            \item Basic offline support for critical features (e.g., appointment viewing, service browsing).  
            \item Synchronization of data once the device reconnects to the internet.  
        \end{itemize}  
    \item Expo-Specific Features:  
        \begin{itemize}  
            \item Built-in support for Expo modules like secure storage for sensitive data.  
            \item Integration with Expo Updates for over-the-air updates.  
        \end{itemize}  
\end{itemize}  

\subsection{Basic Security Implementation}  
\begin{itemize}  
    \item Input validation for all user inputs to prevent common vulnerabilities like SQL injection or XSS.  
    \item Authentication tokens (JWT or similar) to maintain secure sessions.  
    \item Basic data encryption (HTTPS for data in transit, encryption for sensitive data at rest).  
\end{itemize}  

\subsection{Email Integration for Notifications}  
\begin{itemize}  
    \item Automated email notifications for sign-up confirmations, password resets, and appointment reminders.  
    \item Customizable email templates to maintain brand consistency.  
    \item Error-handling mechanisms for failed email deliveries.  
\end{itemize}  

\subsection{Error Handling and Logging}  
\begin{itemize}  
    \item Centralized logging for backend and mobile errors (e.g., using Sentry or similar services).  
    \item User-friendly error messages for known issues.  
    \item Detailed logs for developers to debug and address technical problems effectively.  
\end{itemize}  
