\subsection{Unit Testing}
\begin{itemize}[leftmargin=*]
    \item \textbf{Backend Testing:}
    \begin{itemize}
        \item Use Jest as the primary testing framework for unit tests.
        \item Achieve a minimum of 70\% code coverage across all modules.
        \item Mock external services and dependencies to isolate unit tests.
        \item Test individual functions and methods for expected behavior and edge cases.
        \item Implement database transaction tests to ensure data integrity.
    \end{itemize}
    
    \item \textbf{Frontend Testing:}
    \begin{itemize}
        \item Utilize React Native Testing Library for component testing.
        \item Write tests for component rendering, state management, and event handling.
        \item Ensure coverage for Redux actions, reducers, and selectors.
        \item Test custom hooks and context providers for expected outcomes.
    \end{itemize}
\end{itemize}

\subsection{Integration Testing}
\begin{itemize}[leftmargin=*]
    \item \textbf{GraphQL API Integration:}
    \begin{itemize}
        \item Use libraries like \texttt{Apollo Server Testing} or \texttt{GraphQL Playground} for testing GraphQL queries and mutations.
        \item Validate request and response payloads for all GraphQL operations (queries, mutations, subscriptions).
        \item Test authentication and authorization flows for secure GraphQL endpoints (e.g., ensuring proper token handling).
        \item Ensure proper error handling, including GraphQL-specific errors (e.g., validation errors, permissions issues).
        \item Verify correct response structure and data consistency according to the schema (e.g., ensuring the presence of required fields).
        \item Test edge cases by providing invalid data inputs to ensure proper error messages and status codes.
    \end{itemize}

        \item \textbf{Database Integration:}
    \begin{itemize}
        \item Set up a test database environment for integration tests.
        \item Verify data consistency and relationships across tables.
        \item Test complex queries and data retrieval operations.
        \item Ensure rollback of transactions in case of test failures.
    \end{itemize}
\end{itemize}
    



\subsection{End-to-End (E2E) Testing}
\begin{itemize}[leftmargin=*]
    \item \textbf{Mobile App Testing:}
    \begin{itemize}
        \item Use Detox or Appium for end-to-end testing of mobile applications.
        \item Automate critical user journeys, such as login, navigation, and booking.
        \item Test on real devices and simulators/emulators for comprehensive coverage.
        \item Ensure cross-platform compatibility and responsive design.
    \end{itemize}
    
    \item \textbf{Web Testing:}
    \begin{itemize}
        \item Use Cypress for end-to-end testing of web components.
        \item Validate integration between frontend and backend components.
        \item Ensure smooth navigation and data flow across pages.
        \item Test for performance bottlenecks and loading times.
    \end{itemize}
\end{itemize}

\subsection{Continuous Testing and CI/CD Integration}
\begin{itemize}[leftmargin=*]
    \item \textbf{Automated Testing Pipeline:}
    \begin{itemize}
        \item Integrate testing suites into the CI/CD pipeline for automated execution.
        \item Run unit and integration tests on every pull request to catch regressions early.
        \item Schedule E2E tests to run on staging environments before deployment.
    \end{itemize}
    
    \item \textbf{Reporting and Monitoring:}
    \begin{itemize}
        \item Generate test reports with coverage metrics and test results.
        \item Monitor test execution times and identify slow tests for optimization.
        \item Set up alerts for test failures to ensure quick response and resolution.
    \end{itemize}
\end{itemize}